---
title: Time-Dose Two-parameter Log-Logistic Model (td2pLL)
output: github_document
always_allow_html: true
---



```{r setup, include = FALSE}
# knitr::opts_chunk$set(
#   collapse = TRUE,
#   comment = "#>",
#   fig.path = "man/figures/README-",
#   out.width = "100%"
# )
library(knitr)
library(td2pLL)
```


<!-- badges: start -->
<!-- badges: end -->

The goal of td2pLL is to fit and display time-dose two-parameter log-logistic (td2pLL)  models to appropriate data, e.g. cytotoxicity data. The td2pLL model is defined as 

$$f(t, d) = 100 - 100\frac{d^h}{ED_{50}(t)^h + d^h}$$ with
$$ED_{50} =\Delta \cdot t^{-\gamma} + C_0$$.

## Installation


``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jcduda/td2pLL")
```
## Example 1: Plot a td2pLL model fit

This is a basic example which shows you how to solve a common problem:

```{r example1}
library(td2pLL)
data(cytotox)
# Use subset of compound ASP
data_subset <- cytotox[cytotox$compound == "ASP", c("expo", "dose", "resp")]
colnames(data_subset)[1] <- "time"
fit <- fit_td2pLL(data = data_subset)
plot(fit)


```



```{r}
# change scale of dose axis: 
plot(fit, xaxis_scale = "linear")

# Details on fit:
summary(fit)
# Calculate ED50 values at different (exposure) times:
td2pLL:::get_ED50s(coefs = coef(fit), times = c(1, 2, 3))

```


## Example 2: Use two-step pipeline for conditional time-dose modeling

If you are not sure if you need to model time-dependency, you can use the
two-step anova-based pipeline using `TDR()`.
In an initial step, via nested anova it is checked if the time has an influence.
Specifically, a 2pLL model with upper and lower limit set to 100 and 0, respectively,
that ignores the epxosure time component is the null model.
The full model is a 2pLL model where for each exposure time, a different
$ED_{50}$ parameter is fitted. Only the $h$ parameter is shared across exposure 
times.
If the anova test between these nested models is significant, an effect of the
exposure time is assumed to be true. 
In thas case, a td2pLL model is fitted in the second step, the modeling step.
If the pre-test does not yield a significant result, then the regualr 2pLL model
with upper and lower limit 100 and 0, respectively, is fitted.


For the data of the above chosen compound, ASP, no influence of the
exposure time pn the viability was detected.

```{r}
TDR_res <- TDR(data = data_subset)
TDR_res
plot(TDR_res$fit)
```

If we instead look at the measurements for the CHL compound, the pre-test
suggests to model the time-dependency.

```{r}
data_subset <- cytotox[cytotox$compound == "CHL", c("expo", "dose", "resp")]
colnames(data_subset)[1] <- "time"
TDR_res <- TDR(data = data_subset)
TDR_res$pretest
plot(TDR_res$fit)
```

