---
title: 'Optimal Designs td2pLL: Numerical Problems'
author: "Julia Duda"
date: "14.04.2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(devtools)
library(ggplot2)
library(plotly)
library(knitr)
load_all()
```

## Overview

Figure otu numerical problems in calculating the D-optimal design for
a td2pLL model.

The model:

```{r, echo = TRUE}
my_theta = c(h=2, delta=0.2, gamma=1.3, c0=0.2)
plot_td2pLL(td2pLL_coefs = my_theta, dose_lim = c(0, 1), time_lim = c(1, 10),
            xaxis_scale = "linear")
```
The model formula is

\[f(d, t) = 100 - 100 \frac{d^h}{ED_{50}(t)^h + d^h}\] with
\[ED_{50}(t) = \Delta \cdot t^{-\gamma} + C_0\]


We now calculate (optimal) designs with various number of
support points and settings for the particle swarm optimization algorithm.

For the intercept however, we assume that is is not fixed, i.e. $E_0$ is not
100.
This is required for the optimal design calculation as otherwise, no
design points at dose=0 will be contained in the optimal design.

We vary the number of support points between

- $k \in \{4, 5, ... , 10\}$

and vary the number iterations between

- $n_{iter} \in \{100, 200, 300\}$

At each combination, we use, for the beginning 

- $n_{rep} = 5$ repetitions

only for a first impression on instability.

## Quick Start

From an initial analysis, the $k = 9$ seemed to be optimal. Then the
numerical problems where discovered.

```{r, echo = FALSE}

plot_td2pLL_des <- function(des, weights, color = NULL, plotly = TRUE) {
  df <- cbind.data.frame(des, weights)
  colnames(df)[1:2] <- c("time", "dose")
  
  if(is.null(color)){
    df$color = "blue"
  } else {
    stopifnot(length(color) == nrow(des))
    df$color <- color
  }
  
 p <- df %>% ggplot(., 
               aes(x = dose, y = time, size = weights)) +
   coord_cartesian(xlim = c(0, 1), ylim = c(1, 10)) + 
   geom_point(alpha = 0.5, fill = df$color) +
   scale_size_continuous(limits = c(0, 1)) +
   # scale_size(range = c(0, 4)) +
   theme_minimal() +
   labs(title = paste0("Number of points: ",length(weights))) 
 if(plotly) {
   p <-  as_widget(ggplotly(p))
 } 
 
 return(p)
 
  
}

quick_plot <- function(pso_des){
  des <- pso_des$supPoints
  weights <- pso_des$weights
  return(plot_td2pLL_des(des = des, weights = weights))
  
}


```

## 100 Iterations, 300 particles
Calculate optimal designs, one per number of points $k$ and 100 iterations and 300 particles:

```{r}
set.seed(1905)

all_k <- 4:10
# STOPPED HERE!
all_rep <- 1:3
all_num_it <- c(100, 200, 300)

all_combs <- expand.grid(k = all_k,
                         rep = all_rep,
                         num_it = all_num_it)

apply(all_combs[1:2,], 1, function(comb){
  opt_des <-  opt_des_td2pLL(nPoints = comb["k"],
                             theta = my_theta,
                             control = list(numIt = comb["num_it"],
                                            numPart = 300, setProgressBar = TRUE))
})

res_it_100_part_300 <- vector(mode = "list", length = length(all_k))
names(res_it_100_part_300) <- paste0("k_", all_k)
for(i in 1:length(all_k)){
  res_it_100_part_300[[i]] <-
 opt_des_td2pLL(nPoints = all_k[i], theta = my_theta, control = list(numIt = 100, numPart = 300, setProgressBar = TRUE))

}

save(res_it_100_part_300, file="res_it_100_part_300.RData")
load("res_it_100_part_300.RData")

```

```{r}
plot_list <- htmltools::tagList()
for (i in 1:length(res_it_100_part_300)) 
  plot_list[[i]] = as_widget(quick_plot(res_it_100_part_300[[i]]) )
plot_list
```

### Equivalence plot

```{r}
td2pLL::dcrit_equ_plot_td2pLL(res_it_100_part_300$k_9,
                              theta = my_theta, return_values = F,
                              title = "Points: 9, Iterations: 100")
```



## 200 Iterations, 300 particles
```{r}
# set.seed(1905)
# 
# all_k <- 3:13
# res_it_200_part_300 <- vector(mode = "list", length = length(all_k))
# names(res_it_200_part_300) <- paste0("k_", all_k)
# for(i in 1:length(all_k)){
#   res_it_200_part_300[[i]] <-
#  opt_des_td2pLL(nPoints = all_k[i], theta = my_theta, control = list(numIt = 200, numPart = 300, setProgressBar = TRUE))
#   
# }
# 
# save(res_it_200_part_300, file="res_it_200_part_300.RData")
load("res_it_200_part_300.RData")

```

```{r}

plot_list <- htmltools::tagList()
for (i in 1:length(res_it_200_part_300)) 
  plot_list[[i]] = as_widget(quick_plot(res_it_200_part_300[[i]]) )
plot_list
```

### Equivalence plot

```{r}
td2pLL::dcrit_equ_plot_td2pLL(res_it_200_part_300$k_9,
                              theta = my_theta, return_values = F,
                              title = "Points: 9, Iterations: 200")
```
