---
title: 'Optimal Designs td2pLL: Numerical Problems'
author: "Julia Duda"
date: "14.04.2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(devtools)
library(ggplot2)
library(plotly)
library(knitr)
library(tidyverse)
load_all()
```

## Overview

Figure otu numerical problems in calculating the D-optimal design for
a td2pLL model.

The model:

```{r, echo = TRUE}
my_theta = c(h=2, delta=0.2, gamma=1.3, c0=0.2)
plot_td2pLL(td2pLL_coefs = my_theta, dose_lim = c(0, 1), time_lim = c(1, 10),
            xaxis_scale = "linear")
```
The model formula is

\[f(d, t) = 100 - 100 \frac{d^h}{ED_{50}(t)^h + d^h}\] with
\[ED_{50}(t) = \Delta \cdot t^{-\gamma} + C_0\]


We now calculate (optimal) designs with various number of
support points and settings for the particle swarm optimization algorithm.

For the intercept however, we assume that is is not fixed, i.e. $E_0$ is not
100.
This is required for the optimal design calculation as otherwise, no
design points at dose=0 will be contained in the optimal design.

## 1. Simulation Setup

We vary the number of support points between

- $k \in \{4, 5, ... , 10\}$

and vary the number iterations between

- $n_{iter} \in \{100, 200, 300\}$

At each combination, we use, for the beginning 

- $n_{rep} = 3$ repetitions

only for a first impression on instability.


```{r, run_sim}
# set.seed(1905)
# 
# all_k <- 4:10
# all_rep <- 1:3
# all_num_it <- c(100, 200, 300)
# 
# all_combs <- expand.grid(k = all_k,
#                          num_it = all_num_it,
#                          rep = all_rep)
# 
# # comb <- all_combs[9,] %>% unlist
# sim_res <- apply(all_combs, 1, function(comb){
#   opt_des <-  opt_des_td2pLL(nPoints = comb["k"],
#                              theta = my_theta,
#                              control = list(numIt = comb["num_it"],
#                                             numPart = 300, setProgressBar = FALSE))
#   
#   opt_des_df <- cbind(
#              k = comb["k"],
#              num_it = comb["num_it"],
#              rep = comb["rep"],
#              time = opt_des$supPoints[, 1],
#              dose = opt_des$supPoints[, 2],
#              weights = opt_des$weights,
#              log10_value = log10(max(opt_des$value, 1)))
#   
#   return(opt_des_df)
# })

```

```{r}

# sim_res <-  do.call(rbind.data.frame, sim_res)
# 
# sim_res <- sim_res %>% group_by(k, num_it, rep) %>%
#   mutate(sim_id = group_indices()) %>%
#   arrange(k, num_it, rep) %>%
#   select(sim_id, everything()) %>%
#   ungroup()
# 
# sim_res <- sim_res %>% mutate_at(1:4, as.character) %>%
#   mutate(k = factor(k, levels = all_k))
# 
# save(sim_res, file = "optDes_sim_res_01.RData")
load("optDes_sim_res_01.RData")

```

## 1. Simulation results

Optimal designs for different $k$ and number of iterations
For each combination there are three replicates.
All three replicates are in one plot (distinguished with colors).

One can see that the algirithm has highly varying results.

```{r, fig.width=10, fig.height=10}

sim_res %>%
ggplot(., aes(x = dose, y = time, size = weights, color =  rep)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 1)) +
  facet_grid( k~ num_it)
```


Unfortunately, there is no clear pattern visible \textit{on first glance}.

In the following, we look at the 10 results with the largest
value for the D-optimality criterion (on $\log_{10}$ scale):

```{r}
n_top <- 10

n_top_des <- sim_res %>% arrange(by = desc(log10_value)) %>%
  group_by(log10_value, sim_id) %>% 
  mutate(group_id = cur_group_id()) %>%
  ungroup() %>% 
  filter(group_id >= max(group_id) - n_top + 1)
  
n_top_des %>%
ggplot(., aes(x = dose, y = time, size = weights, color =  rep)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 1)) +
  facet_grid( k~ num_it)
  

```

### Best design found: k=7 is promising

The very best design seems to be this one $k=7$ and 300 iterations:


```{r}
top_des <- n_top_des %>%
  filter(log10_value == max(log10_value)) 
  
p <- ggplot(top_des, aes(x = dose, y = time, size = weights, color =  rep)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 1)) +
  facet_grid( k~ num_it, labeller = "label_both") +
labs(title = paste0("Log10 D-crit value: ", round(top_des$log10_value[1], 4)))
ggplotly(p)
  

```
The equivalence plot for this design:

```{r, des_to_list}
des_to_list <- function(des_df){
  des_list <- list(
    value =  des_df$log10_value[1],
    weights = des_df$weights,
    supPoints = as.data.frame(des_df[, c("time", "dose")])
  )
  return(des_list)
}
```


```{r, fig.width=10, fig.height=10}
par(mfrow = c(2, 2))
top_des_equ <- dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta,
                                      n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 160, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 120, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 60, n_grid = 50)

```

\textbf{Seven points actualy seems to be correct!}
Six "peaks" in the surface and one point alongside the time=0 edge!!!

Also, the optimal weights seem to be:
1/5, 2/15, 2/15, ..., 2/15


### 2. Simulation: Focus: k = 7

We add a second analysis where we fix $k=7$ as number of support points
and instead vary the 
- number of iterations in \{200, 300\} and the
- number of particles in \{50, 100, 300\}

and allow us to have
- 5 repicates

```{r, run_sim_02}
# set.seed(1905)
# 
# all_k <- 7
# all_rep <- 1:5
# all_num_it <- c(200, 300)
# all_num_part <- c(50, 100, 300)
# 
# all_combs <- expand.grid(k = all_k,
#                          num_it = all_num_it,
#                          num_part = all_num_part,
#                          rep = all_rep)
# 
# # comb <- all_combs[1,] %>% unlist
# sim_02_res <- apply(all_combs, 1, function(comb){
#   opt_des <-  opt_des_td2pLL(nPoints = comb["k"],
#                              theta = my_theta,
#                              control = list(numIt = comb["num_it"],
#                                             numPart = comb["num_part"],
#                                             setProgressBar = FALSE))
# 
#   opt_des_df <- cbind(
#              k = comb["k"],
#              num_it = comb["num_it"],
#              num_part = comb["num_part"],
#              rep = comb["rep"],
#              time = opt_des$supPoints[, 1],
#              dose = opt_des$supPoints[, 2],
#              weights = opt_des$weights,
#              log10_value = log10(max(opt_des$value, 1))) %>%
#              as.data.frame()
# 
#   return(opt_des_df)
# })


```


```{r, load_sim_02}
 # sim_02_res <-  do.call(rbind.data.frame, sim_02_res)
 # 
 # sim_02_res <- sim_02_res %>% group_by(num_it, num_part, rep) %>%
 #   mutate(sim_id = group_indices()) %>%
 #   arrange(num_it, num_part,  rep) %>%
 #   select(sim_id, everything()) %>%
 #   ungroup()
 # 
 #  sim_02_res <- sim_02_res %>% mutate_at(1:5, as.character)  %>%
 #   mutate(num_part = factor(num_part, levels = all_num_part))
 # 
 #  save(sim_02_res, file = "optDes_sim_res_02.RData")
load("optDes_sim_res_02.RData")

```

### Clear estimation difficulties: No optimal design found

```{r, fig.width=10, fig.height=5}

p <- sim_02_res %>%
 ggplot(., aes(x = dose, y = time, size = weights, color =  rep, shape = rep)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 0.5)) +
  facet_grid( num_it~num_part, labeller = "label_both")

ggplotly(p)
```

Again: Very unclear pattern.

Design with best D-criterion:


```{r}
top_des <- sim_02_res %>%
  filter(log10_value == max(log10_value)) 
  
p <- ggplot(top_des, aes(x = dose, y = time, size = weights, color =  rep)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 1)) +
  facet_grid( num_it~num_part, labeller = "label_both") +
  labs(title = paste0("Log10 D-crit value: ", round(top_des$log10_value[1], 4)))
ggplotly(p)
  

```

Does not seem to be optimal, as it does not have the most likely optimal structure
described above.

Corresponding equivalence plot: Clearly not optimal!

```{r, fig.width=10, fig.height=10}
par(mfrow = c(2, 2))
top_des_equ <- dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta,
                                      n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 160, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 120, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 60, n_grid = 50)

```
## 3. Simulation: k=7 and fixed weights

We redo the simulation study 2 but with fixed weights that we assume to be right:
1/5, 2/15, 2/15, ..., 2/15.

```{r, simulation_3_run}
# set.seed(1905)
# 
# all_k <- 7
# all_rep <- 1:5
# all_num_it <- c(200, 300)
# all_num_part <- c(50, 100, 300)
# fixed_weights <- c(1/5, rep(2/15, 6))
# 
# all_combs <- expand.grid(k = all_k,
#                          num_it = all_num_it,
#                          num_part = all_num_part,
#                          rep = all_rep)
# 
# # comb <- all_combs[1,] %>% unlist
# sim_03_res <- apply(all_combs, 1, function(comb){
#   opt_des <-  opt_des_td2pLL(nPoints = comb["k"],
#                              theta = my_theta,
#                              wFixed = fixed_weights,
#                              control = list(numIt = comb["num_it"],
#                                             numPart = comb["num_part"],
#                                             setProgressBar = FALSE))
# 
#   opt_des_df <- cbind(
#              k = comb["k"],
#              num_it = comb["num_it"],
#              num_part = comb["num_part"],
#              rep = comb["rep"],
#              time = opt_des$supPoints[, 1],
#              dose = opt_des$supPoints[, 2],
#              weights = opt_des$weights,
#              log10_value = log10(max(opt_des$value, 1))) %>%
#              as.data.frame()
# 
#   return(opt_des_df)
# })


```


```{r, load_sim_03}
 # sim_03_res <-  do.call(rbind.data.frame, sim_03_res)
 # 
 # sim_03_res <- sim_03_res %>% group_by(num_it, num_part, rep) %>%
 #   mutate(sim_id = cur_group_id()) %>%
 #   arrange(num_it, num_part,  rep) %>%
 #   select(sim_id, everything()) %>%
 #   ungroup()
 # 
 #  sim_03_res <- sim_03_res %>% mutate_at(1:5, as.character)  %>%
 #   mutate(num_part = factor(num_part, levels = all_num_part))
 # 
 #  save(sim_03_res, file = "optDes_sim_res_03.RData")
load("optDes_sim_res_03.RData")

```

### Results Simulation 3: k=7, fixed wights

```{r, fig.width=10, fig.height=5}

p <- sim_03_res %>%
 ggplot(., aes(x = dose, y = time, size = weights, color =  rep, shape = rep)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 0.5)) +
  facet_grid( num_it~num_part, labeller = "label_both")

ggplotly(p)
```

Might be better! Let's look at the best (by D-criterion) result
and its equivalence plot:

```{r}
top_des <- sim_03_res %>%
  filter(log10_value == max(log10_value)) 
  
p <- ggplot(top_des, aes(x = dose, y = time, size = weights, color =  rep)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 1)) +
  facet_grid( num_it~num_part, labeller = "label_both") +
  labs(title = paste0("Log10 D-crit value: ", round(top_des$log10_value[1], 4)))
ggplotly(p)
  
```

Same value (9.6074) for D-criterion as best design of SImulation 1!
Same pattern, but as presumed, the time value for dose=0 is arbitrary,
it just has to obtain the bigger weight: 0.20.

### Top 10 best designs of Simulation 3

```{r}
n_top <- 10

n_top_des <- sim_03_res %>% arrange(by = desc(log10_value)) %>%
  group_by(log10_value, sim_id) %>% 
  mutate(group_id = cur_group_id()) %>%
  ungroup() %>% 
  filter(group_id >= max(group_id) - n_top + 1)
  
p <- n_top_des %>%
ggplot(., aes(x = dose, y = time, size = weights, color =  rep, label = log10_value)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 1)) +
  facet_grid( num_it~num_part, labeller = "label_both")

ggplotly(p)
  

```

300 particles and 300 iterations seems to be the best option.

Equivalence plot of the best design of simulation 3:

```{r, fig.width=10, fig.height=10}
par(mfrow = c(2, 2))
top_des_equ <- dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta,
                                      n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 160, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 120, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta, return_values = F,
                                     plot_phi = 30, plot_theta = 60, n_grid = 50)

```



## Simulation 4: Try with (maybe) easier design and fixed weights

Additionally try with a model where I guess it is easier to estimate the 
parameters (because of a stronger influence of time).

```{r, echo = TRUE}
my_theta_2 = c(h=2, delta=0.7, gamma=0.5, c0=0.1)
plot_td2pLL(td2pLL_coefs = my_theta_2, dose_lim = c(0, 1), time_lim = c(1, 10),
            xaxis_scale = "linear")
```


```{r, simulation_4_run}
# set.seed(1905)
# 
# all_k <- 7
# all_rep <- 1:5
# all_num_it <- c(200, 300)
# all_num_part <- c(50, 100, 300)
# fixed_weights <- c(1/5, rep(2/15, 6))
# 
# all_combs <- expand.grid(k = all_k,
#                          num_it = all_num_it,
#                          num_part = all_num_part,
#                          rep = all_rep)
# 
# # comb <- all_combs[1,] %>% unlist
# sim_04_res <- apply(all_combs, 1, function(comb){
#   opt_des <-  opt_des_td2pLL(nPoints = comb["k"],
#                              theta = my_theta_2,
#                              wFixed = fixed_weights,
#                              control = list(numIt = comb["num_it"],
#                                             numPart = comb["num_part"],
#                                             setProgressBar = FALSE))
# 
#   opt_des_df <- cbind(
#              k = comb["k"],
#              num_it = comb["num_it"],
#              num_part = comb["num_part"],
#              rep = comb["rep"],
#              time = opt_des$supPoints[, 1],
#              dose = opt_des$supPoints[, 2],
#              weights = opt_des$weights,
#              log10_value = log10(max(opt_des$value, 1))) %>%
#              as.data.frame()
# 
#   return(opt_des_df)
# })


```


```{r, load_sim_04}
 # sim_04_res <-  do.call(rbind.data.frame, sim_04_res)
 # 
 # sim_04_res <- sim_04_res %>% group_by(num_it, num_part, rep) %>%
 #   mutate(sim_id = cur_group_id()) %>%
 #   arrange(num_it, num_part,  rep) %>%
 #   select(sim_id, everything()) %>%
 #   ungroup()
 # 
 #  sim_04_res <- sim_04_res %>% mutate_at(1:5, as.character)  %>%
 #   mutate(num_part = factor(num_part, levels = all_num_part))
 # 
 #  save(sim_04_res, file = "optDes_sim_res_04.RData")
load("optDes_sim_res_04.RData")

```


### Results Simulation 4: Easier model, k=7, fixed wights

```{r, fig.width=10, fig.height=5}

p <- sim_04_res %>%
 ggplot(., aes(x = dose, y = time, size = weights, color =  rep, shape = rep,
               label = log10_value)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 0.5)) +
  facet_grid( num_it~num_part, labeller = "label_both")

ggplotly(p)
```

Also with the presumably easier model, the results are highly varying.
We look at the 10 best results based on the D-optimality criterion:

### Top 10 best designs of Simulation 4

```{r}
n_top <- 10

n_top_des <- sim_04_res %>% arrange(by = desc(log10_value)) %>%
  group_by(log10_value, sim_id) %>% 
  mutate(group_id = cur_group_id()) %>%
  ungroup() %>% 
  filter(group_id >= max(group_id) - n_top + 1)
  
p <- n_top_des %>%
ggplot(., aes(x = dose, y = time, size = weights, color =  rep, label = log10_value)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 1)) +
  facet_grid( num_it~num_part, labeller = "label_both")

ggplotly(p)
  

```

### Best design fo simulation 4:

The design fulfils the structure.

```{r}
top_des <- sim_04_res %>%
  filter(log10_value == max(log10_value)) 
  
p <- ggplot(top_des, aes(x = dose, y = time, size = weights, color =  rep)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 1)) +
  facet_grid( num_it~num_part, labeller = "label_both") +
  labs(title = paste0("Log10 D-crit value: ", round(top_des$log10_value[1], 4)))
ggplotly(p)
  
```

And it is optimal:

```{r, fig.width=10, fig.height=10}
par(mfrow = c(2, 2))
top_des_equ <- dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2,
                                      n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 160, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 120, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 60, n_grid = 50)

```


The plot is not fully below zero. The peak is at the in-between time value.
It might be, because they are not even levelled (on the time-axis).


## Simulation 5: Itertions=1000, particles=1000
Also try: Very large number of iterations and particles:

```{r, siulation_5_run}

# set.seed(1905)
# 
# all_k <- 7
# all_rep <- 1:10
# all_num_it <- 1000
# all_num_part <- 1000
# fixed_weights <- c(1/5, rep(2/15, 6))
# 
# all_combs <- expand.grid(k = all_k,
#                          num_it = all_num_it,
#                          num_part = all_num_part,
#                          rep = all_rep)
# 
# # comb <- all_combs[1,] %>% unlist
# sim_05_res <- apply(all_combs, 1, function(comb){
#   opt_des <-  opt_des_td2pLL(nPoints = comb["k"],
#                              theta = my_theta_2,
#                              wFixed = fixed_weights,
#                              control = list(numIt = comb["num_it"],
#                                             numPart = comb["num_part"],
#                                             setProgressBar = FALSE))
# 
#   opt_des_df <- cbind(
#              k = comb["k"],
#              num_it = comb["num_it"],
#              num_part = comb["num_part"],
#              rep = comb["rep"],
#              time = opt_des$supPoints[, 1],
#              dose = opt_des$supPoints[, 2],
#              weights = opt_des$weights,
#              log10_value = log10(max(opt_des$value, 1))) %>%
#              as.data.frame()
# 
#   return(opt_des_df)
# })

```


```{r, load_sim_05}
#  sim_05_res <-  do.call(rbind.data.frame, sim_05_res)
# 
#  sim_05_res <- sim_05_res %>% group_by(num_it, num_part, rep) %>%
#    mutate(sim_id = cur_group_id()) %>%
#    arrange(num_it, num_part,  rep) %>%
#    select(sim_id, everything()) %>%
#    ungroup()
# 
#   sim_05_res <- sim_05_res %>% mutate_at(1:5, as.character)  %>%
#    mutate(num_part = factor(num_part, levels = all_num_part))
# 
# save(sim_05_res, file = "optDes_sim_res_05.RData")
load("optDes_sim_res_05.RData")

```

### Results Simulation 5

For 4 out of 10 replications, the optial design was achieved now
(Replication 1, 5, 6, 7).

Also: Seems like time value is not the same for the two dose values in between!

```{r, fig.width=10, fig.height=5}

p <- sim_05_res %>%
 ggplot(., aes(x = dose, y = time, size = weights, color =  rep,
               label = log10_value)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 0.5)) 

ggplotly(p)
```
### Simulation 5: Equivalence plot

```{r, fig.width=10, fig.height=10}
top_des <- sim_05_res %>%
  filter(log10_value == max(log10_value)) 

par(mfrow = c(2, 2))
top_des_equ <- dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2,
                                      n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 160, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 120, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 60, n_grid = 50)


```

Weird that the equivalence plot suggests non-optimality.


## Simulation 6: IterationsParticles=1000, no fixed weights:



Try again with non-fixed weights and iterations=particles=1000:

```{r, simulation_6_run}
# 
# set.seed(1905)
# 
# all_k <- 7
# all_rep <- 1:10
# all_num_it <- 1000
# all_num_part <- 1000
# 
# 
# all_combs <- expand.grid(k = all_k,
#                          num_it = all_num_it,
#                          num_part = all_num_part,
#                          rep = all_rep)
# 
# # comb <- all_combs[1,] %>% unlist
# sim_06_res <- apply(all_combs, 1, function(comb){
#   opt_des <-  opt_des_td2pLL(nPoints = comb["k"],
#                              theta = my_theta_2,
#                              wFixed = NULL,
#                              control = list(numIt = comb["num_it"],
#                                             numPart = comb["num_part"],
#                                             setProgressBar = FALSE))
# 
#   opt_des_df <- cbind(
#              k = comb["k"],
#              num_it = comb["num_it"],
#              num_part = comb["num_part"],
#              rep = comb["rep"],
#              time = opt_des$supPoints[, 1],
#              dose = opt_des$supPoints[, 2],
#              weights = opt_des$weights,
#              log10_value = log10(max(opt_des$value, 1))) %>%
#              as.data.frame()
# 
#   return(opt_des_df)
# })
# 
# ```
# 
# 
# ```{r, load_sim_05}
#  sim_06_res <-  do.call(rbind.data.frame, sim_06_res)
# 
#  sim_06_res <- sim_06_res %>% group_by(num_it, num_part, rep) %>%
#    mutate(sim_id = cur_group_id()) %>%
#    arrange(num_it, num_part,  rep) %>%
#    select(sim_id, everything()) %>%
#    ungroup()
# 
#   sim_06_res <- sim_06_res %>% mutate_at(1:5, as.character)  %>%
#    mutate(num_part = factor(num_part, levels = all_num_part))
# 
# save(sim_06_res, file = "optDes_sim_res_06.RData")
load("optDes_sim_res_06.RData")

```

Top design is replicate 3: Here, it looks again like even levelled
in-between time-value is good.

```{r, fig.width=10, fig.height=5}

p <- sim_06_res %>%
 ggplot(., aes(x = dose, y = time, size = weights, color =  rep,
               label = log10_value)) +
  geom_point(alpha = 0.5) +
  scale_size_continuous(limits = c(0, 0.5)) 

ggplotly(p)
```
```{r, fig.width=10, fig.height=10}
top_des <- sim_06_res %>%
  filter(log10_value == max(log10_value)) 

par(mfrow = c(2, 2))
top_des_equ <- dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2,
                                      n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 160, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 120, n_grid = 50)
dcrit_equ_plot_td2pLL(des = des_to_list(top_des), theta = my_theta_2, return_values = F,
                                     plot_phi = 30, plot_theta = 60, n_grid = 50)


```



## Idea

Incorporating the structure of having:

two points at lowest time, two at highest, two in between (but at the same
time value!) might improve the algorithm!

Also: Deep dive into the particle swarm optimizer to better understand
the role of the hyperparameters beta and gamma!


